Entrainment of low Mach number thermals in stratified domains

### 2019-05-02 tex/stratified_thermals.tex
some paper updates, starts getting 3D data in

\appendix
\section{Thermal Tracking}
\label{appendix:tracking}

@@

%\begin{deluxetable*}{c c c c c c c c c c c c c c c}
%\tabletypesize{\footnotesize}
%\caption{Table of simulation information
%\label{table:simulation_info}
%}
%\tablehead{																																															
%\colhead{Ra$_{\text{top}}$}	&	\colhead{Ta$_{\text{top}}$}	&	\colhead{Ro$_{\text{p, top}}$}	&	\colhead{Ra$_{\text{mid}}$}	&	\colhead{Ta$_{\text{mid}}$}	&	\colhead{Ro$_{\text{p, mid}}$}	&	\colhead{\con}	&	\colhead{$\mathcal{S}$}	&	\colhead{$L_x/L_z$}	&	\colhead{(nz,	nx,	ny)}	&					\colhead{Ro}      	&	\colhead{Re$_{\parallel}$} 	&	\colhead{Re$_{\perp}$}	&	\colhead{Nu}      	}														
%\startdata																																															
%\multicolumn{3}{l}{\textbf{Constant \pro$\,$, path III}}\\
%1.8	$\times 10^{	5	}$	&	4.1	$\times 10^{	7	}$	&	0.60	&	1.4	$\times 10^{	7	}$	&	3.0	$\times 10^{	9	}$	&	1.03	&	0.067	&	1.1	&	0.51	&	(256,		32,		32)	&	0.015	&	19.4	&	2.5	&	1.2	\\				
%1.2	$\times 10^{	9	}$	&	5.2	$\times 10^{	12	}$	&	0.60	&	9.2	$\times 10^{	10	}$	&	3.8	$\times 10^{	14	}$	&	1.03	&	0.015	&	3.0	&	0.07	&	(2048,		64,		64)	&	0.026	&	1771	&	32.0	&	15.4	\\				
%5.2	$\times 10^{	2	}$	&	4.6	$\times 10^{	3	}$	&	0.96	&	3.8	$\times 10^{	4	}$	&	3.4	$\times 10^{	5	}$	&	1.64	&	0.333	&	1.13	&	2.28	&	(64,		64,		64)	&	0.074	&	4.2	&	2.5	&	1.2	\\				
%3.8	$\times 10^{	8	}$	&	3.1	$\times 10^{	11	}$	&	0.96	&	2.8	$\times 10^{	10	}$	&	2.3	$\times 10^{	13	}$	&	1.64	&	0.035	&	6.0	&	0.12	&	(2048,		64,		64)	&	0.129	&	3906	&	113	&	66.9	\\				
%7.9	$\times 10^{	1	}$	&	1.0	$\times 10^{	2	}$	&	1.58	&	5.8	$\times 10^{	3	}$	&	7.4	$\times 10^{	3	}$	&	2.70	&	0.888	&	1.56	&	4.44	&	(64,		64,		64)	&	0.303	&	4.4	&	4.9	&	1.7	\\				
%1.4	$\times 10^{	7	}$	&	9.7	$\times 10^{	8	}$	&	1.58	&	1.0	$\times 10^{	9	}$	&	7.2	$\times 10^{	10	}$	&	2.70	&	0.119	&	10.0	&	0.30	&	(512,		128,		128)	&	0.376	&	1257	&	94.9	&	40.1	\\				
%\hline																																															
%\multicolumn{3}{l}{\textbf{Constant \con$\,$, path II}}\\
%8.6	$\times 10^{	4	}$	&	8.6	$\times 10^{	6	}$	&	0.74	&	6.3	$\times 10^{	6	}$	&	6.3	$\times 10^{	8	}$	&	1.26	&	0.1	&	1.47	&	0.68	&	(128,		128,		128)	&	0.051	&	40.2	&	6.7	&	2.2	\\				
%2.6	$\times 10^{	6	}$	&	2.6	$\times 10^{	8	}$	&	1.13	&	1.9	$\times 10^{	8	}$	&	1.9	$\times 10^{	10	}$	&	1.93	&	0.1	&	4.64	&	0.39	&	(256,		512,		512)	&	0.27	&	565	&	53.2	&	33.3	\\				
%1.4	$\times 10^{	3	}$	&	1.6	$\times 10^{	4	}$	&	1.01	&	1.1	$\times 10^{	5	}$	&	1.2	$\times 10^{	6	}$	&	1.72	&	0.3	&	1.47	&	1.90	&	(64,		128,		128)	&	0.124	&	11.3	&	5.4	&	1.8	\\				
%1.1	$\times 10^{	6	}$	&	1.2	$\times 10^{	7	}$	&	2.29	&	7.8	$\times 10^{	7	}$	&	8.6	$\times 10^{	8	}$	&	3.93	&	0.3	&	14.7	&	0.65	&	(192,		384,		384)	&	0.808	&	529	&	83.5	&	27.3	\\				
%5.5	$\times 10^{	1	}$	&	5.5	$\times 10^{	1	}$	&	1.65	&	4.0	$\times 10^{	3	}$	&	4.0	$\times 10^{	3	}$	&	2.82	&	1.0	&	1.47	&	4.84	&	(64,		128,		128)	&	0.303	&	3.6	&	4.4	&	1.5	\\				
%2.8	$\times 10^{	6	}$	&	2.8	$\times 10^{	6	}$	&	6.39	&	2.0	$\times 10^{	8	}$	&	2.0	$\times 10^{	8	}$	&	10.93	&	1.0	&	100	&	0.82	&	(256,		512,		512)	&	3.357	&	1099	&	220	&	46.6	\\				
%\hline																																															
%\multicolumn{3}{l}{\textbf{Constant $\mathcal{S}$, path I}}\\
%1.9	$\times 10^{	1	}$	&	1.1	$\times 10^{	-1	}$	&	10.00	&	1.4	$\times 10^{	3	}$	&	7.9	$\times 10^{		}$	&	17.12	&	13.2	&	2.0	&	9.91	&	(64,		64,		64)	&	3.668	&	3.0	&	10.2	&	1.7	\\				
%3.0	$\times 10^{	6	}$	&	1.1	$\times 10^{	9	}$	&	0.70	&	2.2	$\times 10^{	8	}$	&	8.1	$\times 10^{	10	}$	&	1.20	&	0.052	&	2.0	&	0.30	&	(512,		128,		128)	&	0.053	&	242	&	17.9	&	6.0	\\				
%3.0	$\times 10^{	1	}$	&	2.0	$\times 10^{	-1	}$	&	10.00	&	2.2	$\times 10^{	3	}$	&	1.5	$\times 10^{	1	}$	&	17.12	&	12.2	&	3.0	&	9.48	&	(64,		64,		64)	&	4.418	&	5.0	&	15.5	&	2.1	\\				
%1.3	$\times 10^{	7	}$	&	5.6	$\times 10^{	9	}$	&	0.80	&	9.7	$\times 10^{	8	}$	&	4.2	$\times 10^{	11	}$	&	1.37	&	0.048	&	3.0	&	0.23	&	(512,		128,		128)	&	0.08	&	592	&	33.4	&	13.6	\\				
%\enddata																																															
%\tablecomments{
%Input parameters and output parameters for select simulations are shown. For each of
%the eight paths in Fig. \ref{fig:parameter_space}b, we show information for the lowest and
%highest (Ra, Ta) point on that path. The first six rows show information for constant
%$\pro\,$ paths, the next six for constant \con$\,$ paths, and the last four for constant $\mathcal{S}$ paths.
%We show the input Ra, Ta, and \pro$\,$ at the top of the atmosphere, as well as their
%stratification-weighted values at the midplane of the atmosphere, which provide a more direct
%comparison to Boussinesq values \citep{unnoetall1960}. We also provide the input \con$\,$ at the
%top of the atmosphere, $\mathcal{S}$, aspect ratio ($L_x/L_z$), and coefficient resolution
%(nz, nx, ny). Each dimension of the physical grid is 3/2 the size of the coefficient grid 
%for adequate dealiasing of quadratic nonlinear terms.
%Output values of Ro, Re$_{\parallel}$, Re$_{\perp}$, and Nu are also provided.
%This table in its entirety is published as a supplemental \texttt{.csv} file with this
%manuscript and also online in a Zenodo repository \citep{supp_andersetall2019}.
%}
%\end{deluxetable*}
%

>>>>

\appendix
\section{Thermal Tracking}
\label{appendix:tracking}
We use a thermal tracking algorithm very similar to the one used in 
\citet{lecoanet&jeevanjee2018} and inspired by the work of 
\citet{romps&all2015}.

We begin by measuring the thermal's height versus
time. To do so, we average the domain's entropy profile in radius and azimuth
to create an average profile of entropy with height, and then we use
scipy's brentq function on the derivative of that profile to find its maximum.

Next, we find the best fit of the thermal's height vs. time according to our theory
and derive that fit according to Eqn.~\ref{eqn:theory_velocity} to find the bulk
vertical velocity of the thermal, $w_b$. We then calculate the streamfunction of
the velocity field as in \citet{romps&all2015},
\begin{equation}
\frac{\partial \psi}{\partial r} = 2\pi \rho r (w - w_b),
\end{equation}
with the boundary condition that $\psi = 0$ at $r = 0$. The contour defined by $\psi = 0$
from this solution is taken to be the outline of the thermal, and the volume of the thermal
is taken to be the volume radially inward from that contour.

@@

\begin{deluxetable*}{c c c c c c}
\tabletypesize{\footnotesize}
\caption{Table of simulation information
\label{table:simulation_info}
}
\tablehead{																																															
\colhead{$n_\rho$} & \colhead{$L_{thermal}/H_\rho$} & \colhead{nr or nx = ny} & \colhead{nz} & \colhead{$t_{evolution}$} & \colhead{safety}	}	
\startdata																																															
\multicolumn{3}{l}{\textbf{2D Anelastic Simulations}}\\
0.1 	& 					&	128			& 512			& 45 	&	100	\\
0.5 	& 					&	128			& 512			& 45 	&	100	\\
1	 	& 					&	128			& 512			& 45 	&	100	\\
2	 	& 					&	256			& 512			& 30 	&	100	\\
3	 	& 					&	512			& 1024			& 30 	&	100	\\
4	 	& 					&	1024		& 1024			& 30 	&	100	\\
5	 	& 					&			& 			&  	&		\\
6	 	& 					&			& 			&  	&		\\
7	 	& 					&			& 			&  	&		\\
\multicolumn{3}{l}{\textbf{3D Fully Compressible Simulations}}\\
0.5 	& 					&	256			& 512			& 45 	&	0.6	\\
1	 	& 					&	256			& 512			& 45 	&	0.6	\\
2	 	& 					&	256			& 1024			& 45 	&	0.6	\\
3	 	& 					&	256			& 2048			& 45 	&	0.6	\\
\enddata																																															
\tablecomments{
}
\end{deluxetable*}
